---
title: "Assignment 1.10"
author: "Your Name"
date: "09/12/2025"
output:
  html_document:
    df_print: paged
subtitle: 'CPSC 292 Section ##'
---

### Collaboration team: 

Record who you've worked on the assignment with here. 


## Assignment 1.10 -- Data Frames

```{r setup, include=FALSE}
# Do not alter this section of code!
knitr::opts_chunk$set(echo = TRUE)
```

Write a R code in each chunk (gray space) that provides answers to the following questions. If any questions need direct answers, give them in regular text space (white space).

### Question 1

*Create a data frame that has columns with three different data types.*

```{r}
df <- data.frame("characters" = c("yip", "yip", "yip"), 
                 "numbers" = c(1.2, 3.5, 2.4),
                 "logicals" = c(T, T, F))
```

_Any data frame that works and has three different data types is fine._

### Question 2

*Load the data set warpbreaks, which is a data set based on manufacturing yarn.*

```{r}
data("warpbreaks")

```

*Use it to answer the following questions:*

  a. *What is the mean number of breaks in the study under all conditions?*
  
```{r}
mean(warpbreaks$breaks)
```

  b. *How many observations are in each type of wool? How many observations in each type of tension?* 
  
```{r}
table(warpbreaks$wool)
table(warpbreaks$tension)
```
  
_There are several ways to do this, any that reports all the counts for all groups is fine._
  
  c. *Create two separate vectors with all the breaks in one vector and all the tensions in the other.*
  
```{r}
vec1 <- warpbreaks$breaks
vec2 <- warpbreaks$tension
```
  
  d. *Subset the data frame into a new object that represents only the breaks for tension M.*
  
```{r}
med_tension <- warpbreaks$breaks[warpbreaks$tension == "M"]
```

  e. *Repeat this subsetting into two new objects for only breaks for tension H and tension L.*
  
```{r}
high_tension <- warpbreaks$breaks[warpbreaks$tension == "H"]
low_tension <- warpbreaks$breaks[warpbreaks$tension == "L"]
```

  f. *What are the mean number of breaks for each tension value?*
  
```{r}
mean(low_tension)
mean(med_tension)
mean(high_tension)
```

  g. *If you were in charge of reducing the number of breaks during yarn production, which tension should you set the machines at?* 
  
Your answer here.

  
### Question 3

*The following line of code does not work. Correct the error so that the code returns the mean weight of chicks fed soybean or linseed feed.*
```{r}
stdev(warpbreaks$breaks[warpbreaks$wool == "A" & warpbreaks$tension == "L",])
```

*Explain why your fix works.*

Your answer here. 

Turn in this RMD file.