---
title: "Assignment 3.2"
author: "Your Name"
date: "10/24/2025"
output:
  html_document:
    df_print: paged
subtitle: "CPSC 292 Section ##"
---

## Assignment 3.2 

```{r, include=TRUE}
# Loading required libraries

```


For each part of each question, write code or answer the question in the simplest way. 

### Question 1


*Complete the following steps:*

 a.  *Create a function that will take an object `x` and return the results of the following calculation: 10x^3 + 2x - 3*

```{r, include=TRUE}

```

 b. *Use your function to calculate the result of ten random numbers. Store the results in another object.*
 
```{r, include=TRUE}

```

 c. *Does your function perform a vectorized calculation? How do you know?*
 
The function should be vectorized because it should take a vector and perform the calculation on each item in the vector.

### Question 2

*Write a function that reports the mean price of diamonds in the `diamonds` data set (`ggplot2` package) when given the clarity. Include an example call of your function that is successful.*

```{r, include=TRUE}

```

Must include the example function call, kick back to student if no call.

### Question 3

  a. *The `carnivores` data set in the `geiger` package contains a phylogenetic tree and a data set including species richness by family. Write a small function that retrieves the number of the row in the `dat` member of `carnivores` when given a family name. Include a line that calls your function with the family name Canidae. Hint: `which()` will give you the position number any TRUE results from a test on a vector.*
  
```{r}

```

  b. *Using the function you wrote for a, make a function that reports the species richness of a user-specified family from the `carnivores` data set. Include a line that calls your function with the family name Felidae.*

```{r, include=TRUE}

```


### Question 4

*Write your own function that does any task that requires two inputs from the user.*

```{r, include=TRUE}

```




